Why Donors Donate?

### 2020-08-28 analysis/05_market_simulator.Rmd
Changed Color, Reordered the Tabs, and Commented out the gauges

  ggplotly(df %>% filter(Type == "Market Share") %>%
             mutate(
               Organization = factor(Organization, levels = c(input$ai_id, input$gp_id, input$ox_id, input$rc_id), ordered = TRUE),
               Persona = factor(Persona, levels = c(input$p1_id, input$p2_id, input$p3_id), ordered = TRUE)) %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="", y = "Market Share") + 
             scale_fill_manual(values = c( "#FFC30B", "#006633", "#660000")) +
             theme(legend.position = "right",
                   panel.background = element_blank(),
                   panel.grid.major.y = element_line(color = "#D3D3D3"))
    )
})

@@

Organizations and Personas {.tabset .tabset-fade}
--------------------------------------------------
### Org 1

textInput("ai_id",
          label = "Organization Name",
          value = "Organization 1",
          placeholder = "Enter Organiation Name",
          width = "200px")

selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"),
            width = "200px")

selectInput("ai_fin_trans",
            label = "Select Financial transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"),
            width = "200px")

selectInput("ai_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in financial accountability",
                        "Engages in financial accountability"),
            width = "200px")

selectInput("ai_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government Grants"),
            width = "200px")

selectInput("ai_gov_relat",
            label = "Select Relationship with host government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"),
            width = "200px")

```{r ai gauge}
renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})
```

```{r gp gauge}
renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})
```

```{r ox gauge}
renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(ox_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(ox_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(ox_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})
```

```{r rc gauge}
renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(rc_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(rc_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(rc_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})
```

@@

```{r persona 1 gauge}
renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(ox_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(rc_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#660000"),
        symbol = "%")
})
```

@@

```{r persona 2 gauge}
renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(ox_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(rc_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#660000"),
        symbol = "%")
})
```

@@

```{r persona 3 gauge}
renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)

  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(ox_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})

renderGauge({
  choice = df()
  per_choice = p()

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)

  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  gauge(rc_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#660000"),
        symbol = "%")
})
```

@@

```{r plot ai plot}
# renderPlotly({
#   choice = df()
#   
#     persona1 = p_beta1 # Choose the persona
#   
#   ai_exp_util1 <- round(exp(t(choice[, 3]) %*% as.matrix(persona1)),2)
#   gp_exp_util1 <- round(exp(t(choice[, 4]) %*% as.matrix(persona1)),2)
#   ox_exp_util1 <- round(exp(t(choice[, 5]) %*% as.matrix(persona1)),2)
#   rc_exp_util1 <- round(exp(t(choice[, 6]) %*% as.matrix(persona1)),2)
#   
#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   
#     persona2 = p_beta2 # Choose the persona
#   
#   ai_exp_util2 <- round(exp(t(choice[, 3]) %*% as.matrix(persona2)),2)
#   gp_exp_util2 <- round(exp(t(choice[, 4]) %*% as.matrix(persona2)),2)
#   ox_exp_util2 <- round(exp(t(choice[, 5]) %*% as.matrix(persona2)),2)
#   rc_exp_util2 <- round(exp(t(choice[, 6]) %*% as.matrix(persona2)),2)
#   
#   ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
#   
#       persona3 = p_beta3 # Choose the persona
#   
#   ai_exp_util3 <- round(exp(t(choice[, 3]) %*% as.matrix(persona3)),2)
#   gp_exp_util3 <- round(exp(t(choice[, 4]) %*% as.matrix(persona3)),2)
#   ox_exp_util3 <- round(exp(t(choice[, 5]) %*% as.matrix(persona3)),2)
#   rc_exp_util3 <- round(exp(t(choice[, 6]) %*% as.matrix(persona3)),2)
#   
#   ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
#   
#   data <- c(ai_exp_util1, ai_rate1, 
#             ai_exp_util2, ai_rate2,
#             ai_exp_util3, ai_rate3)
#   
#   
#   df <- as.data.frame(matrix(data, 6, 1))
#   
#   df[,2] <- c("Amnesty International")
#   df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
#   df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
#   colnames(df) <- c('Value', 'Organization', "Type", "Persona")
#   
#   ggplotly(df %>% filter(Type == "Market Share") %>% 
#              ggplot(aes(y = Value, x = Organization, fill = Persona)) +
#              geom_bar(position = "dodge", stat = "identity") +
#              labs(x="") + 
#              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
#              theme(legend.position = "none")
#     )
# })
```

>>>>

  ggplotly(df %>% filter(Type == "Market Share") %>%
             mutate(
               Organization = factor(Organization, levels = c(input$ai_id, input$gp_id, input$ox_id, input$rc_id), ordered = TRUE),
               Persona = factor(Persona, levels = c(input$p1_id, input$p2_id, input$p3_id), ordered = TRUE)) %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="", y = "Market Share") + 
             scale_fill_manual(values = c( "#FFC30B", "#28a153", "#c23838")) +
             theme(legend.position = "right",
                   panel.background = element_blank(),
                   panel.grid.major.y = element_line(color = "#D3D3D3"))
    )
})

@@

Personas And Organizations {.tabset .tabset-fade}
--------------------------------------------------

@@

@@

@@

### Org 1

textInput("ai_id",
          label = "Organization Name",
          value = "Organization 1",
          placeholder = "Enter Organiation Name")

selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

selectInput("ai_fin_trans",
            label = "Select Financial transparency:",
            choices = c("Doesn’t engage in transparency",
                        "Engages in transparency"))

selectInput("ai_account",
            label = "Select Financial Accountability:",
            choices = c("Doesn’t engage in financial accountability",
                        "Engages in financial accountability"))

selectInput("ai_funding",
            label = "Select Funding source:",
            choices = c("Many small private donations",
                        "Handful of wealthy private donors",
                        "Government Grants"))

selectInput("ai_gov_relat",
            label = "Select Relationship with host government",
            choices = c("Friendly relationship with government",
                        "Criticized by government", 
                        "Under government crackdown"))

@@

```{r persona 1 gauge commented}
# renderGauge({
#   choice = df()
#   per_choice = p()
#     
#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
#    
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
# 
#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   gauge(ai_rate,
#         min = 0,
#         max = 100,
#         gaugeSectors(colors = "#FFC30B"),
#         symbol = "%")
# })
# 
# renderGauge({
#   choice = df()
#   per_choice = p()
#   
#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
#    
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
# 
#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   gauge(gp_rate,
#         min = 0,
#         max = 100,
#         gaugeSectors(colors = "#3fad48"),
#         symbol = "%")
# })
# 
# renderGauge({
#   choice = df()
#   per_choice = p()
#   
#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
#    
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
# 
#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   gauge(ox_rate,
#         min = 0,
#         max = 100,
#         gaugeSectors(colors = "#006633"),
#         symbol = "%")
# })
# 
# renderGauge({
#   choice = df()
#   per_choice = p()
#   
#     p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
#    
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
# 
#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   gauge(rc_rate,
#         min = 0,
#         max = 100,
#         gaugeSectors(colors = "#660000"),
#         symbol = "%")
# })
```

```{r persona 2 gauge commented}
# renderGauge({
#   choice = df()
#   per_choice = p()
#     
#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
#    
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta1)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta1)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta1)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta1)),2)
# 
#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   gauge(ai_rate,
#         min = 0,
#         max = 100,
#         gaugeSectors(colors = "#FFC30B"),
#         symbol = "%")
# })
# 
# renderGauge({
#   choice = df()
#   per_choice = p()
#   
#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
#    
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta2)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta2)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta2)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta2)),2)
# 
#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   gauge(gp_rate,
#         min = 0,
#         max = 100,
#         gaugeSectors(colors = "#3fad48"),
#         symbol = "%")
# })
# 
# renderGauge({
#   choice = df()
#   per_choice = p()
#   
#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
#    
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
# 
#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   gauge(ox_rate,
#         min = 0,
#         max = 100,
#         gaugeSectors(colors = "#006633"),
#         symbol = "%")
# })
# 
# renderGauge({
#   choice = df()
#   per_choice = p()
#   
#     p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])
#    
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(p_beta3)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(p_beta3)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(p_beta3)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(p_beta3)),2)
# 
#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   gauge(rc_rate,
#         min = 0,
#         max = 100,
#         gaugeSectors(colors = "#660000"),
#         symbol = "%")
# })
```
